---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Fill in the code chunks for following question and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 
4. Solo work, open book & open notes - This part of the exam is open book, open notes. You may use the textbook, your own notes, and any pre-existing resources. You must not use communicate with others - in person, using online forums, social media, Slack, WeChat, GroupMe, etc. If you have concerns, contact me directly so I can advise you. 
5. Partial credit - If you can't get your code to work 100% correctly, you can often earn partial credit. To get partial credit you need to show that you know there is a problem and describe it. The better you can describe the problem, the more partial credit you can earn, because it helps demonstrate your knowledge and skill.

### Q1. (10pts) Write several lines of code: for each element in a list x, if the element is a character, print "error", else print the element itself. For example, if we have list x list(24,66,‘nodata’,74,'NA'), the function will print 24,66,error,74,error. Hint: you can use typeof to determine if an object is a character: typeof(obj) == "character".

```{r}

  x <- list(24, 33, 75, 'nodata', TRUE, 'NA')

  printIfElse <- function(x) {
      if (typeof(x) == 'character') {
        print("Error")
      } else {
        print(x)
      }
  }
  
  printIfElse(x)

```

### Q2. (10pts)  Create a function that can convert fahrenheit to celsius. The formula is (F-32)*5/9 = C. Fill in the function body. There is a test case to convert fahrenheit 86 to celsius. 
```{r}
ftoc <- function(x){
  C <- c((x-32)*5/9)
  C
}

ftoc(86)
```

### Q3. (10pts) Read the file '2016.csv' to a dataframe. Check the first 5 lines of the data. 
```{r}

  setwd('/Users/rahulsagi/Downloads')
  csv2016 <- read.csv('2016.csv')
  head(csv2016, 5)

```

### Q4. (10pts) Use the dataframe in Q3. Compute the average Hapiness_Score for countries in North America. 
```{r}

  summary(csv2016)
  mean(csv2016[which(csv2016$Region == 'North America'), 'Happiness_Score'])

```

### Q5. (10pts) Use the dataframe in Q3. Write code to compute the difference in Generosity between United States and Mexico.
```{r}

  genorosityCountries <- subset(csv2016, select = c('Generosity', 'Country'))
  generosityUSAndMexico <- subset(genorosityCountries, (Country == 'Mexico' | Country == 'United States'))
  generosityUSAndMexico
  ### 0.41077	United States		
  ### 0.11735	Mexico
  differanceGenerosity <- c(.41077 - .11735)
  differanceGenerosity
  
  generosityUSAndMexico <- subset(genorosityCountries, (Country == 'Mexico' | Country == 'United States'), select = c('Generosity'))
  differanceGenerosity <- generosityUSAndMexico[1,1] - generosityUSAndMexico[2,1]
  differanceGenerosity
  

```

### Q6. (10pts) Use the dataframe in Q3. Plot the dataframe columns Happiness_Rank and Happiness_Score as a line graph
```{r}

  plot(Happiness_Rank~Happiness_Score, data = csv2016, type = "b", pch = 10, 
     col = "red", xlab = "Happiness_Score", ylab = "Happiness_Rank")

```

### Q7. (10pts) Use the dataframe in Q3. Plot the scatter plot matrix for the four variables: Family, Life_Expectancy,Freedom, Trust, Generosity
```{r}

  pairs(~Family + Life_Expectancy + Freedom + Generosity, data = csv2016, main = "Scatter Plot Matrix Graph For CSV2016")
```

### Q8. (10pts) Get a subset of data with countries from Region of "Western Europe" and "North America" and "Eastern Asia".
```{r}

  summary(csv2016)
  regionCountries <- subset(csv2016, (Region == 'North America' | Region == 'Western Europe' | Region == 'Eastern Asia'))
  regionCountries

```
### Q9. (Bonus 10pts) Use the subset data in Q8. Draw a scatter plot with Government_Corruption in the x-axis, Freedom in the y-axis, and the points are colored by region. 
```{r}

  plot(Freedom~Government_Corruption, data = regionCountries, main = "Government Corruption Anf Freedom Colored On Region", xlab = "Government_Corruption", ylab = "Freedom", col = Region)

```

### Q10. (10pts) Build a linear regression model: predict Hapiness_Score with variables GDP_per_Capita, Family, Life_Expectancy and Freedom. 
```{r}

  predictHappiness <- lm(Happiness_Score~GDP_per_Capita + Family + Life_Expectancy + Freedom, data = csv2016)

```
### Q11. (10pts) Get a summary of the model. Answer the following questions out of the code chunk: what is the adjusted R-squared? What is the coefficient of GDP_per_Capita?
```{r}

  summary(predictHappiness)

```

The adjusted R-Squared is .7752. The coefficient of GDP_per_Capita is .000381 which means that there is a significant relationship between the Happiness Score and GDP_per_Capita. 
